Replication Survey

### 2023-05-22 docs/manuscript/manuscript.tex

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=282 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 17.7 percent, the response rate was 11.3 percent, yielding a cooperation rate of 64.0 percent. 
The refusal rate was 6.4 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly balanced across disciplinary subfields, but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%). 
Different methodological approaches were well represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
\begin{itemize}
    \item Coded analysis of Q6
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Replication - Chances and motivations}
Q12-14 Researcher perspectives on frequency of replication
\begin{itemize}
    \item Q12 - Geographic researchers do not believe many studies in their field have been replicated. Respondents estimated that on average a quarter of recent studies in their sub-field have be replicated. However, the distribution was strongly right skewed with a median resposne of 20\% and a heavy tail of responses (46.9\%) estimating below 10\% of recent studies have been replicated.
    \item Q13 - Respondents estimated that half of the recent studies in their sub-field could be replicated (55.0\%, $\sigma = 24.3\%$). While centered on 55\% responses were fairly evenly dispersed from 0-100 indicating no clear common belied about this value. 
    \item Q14 - Collectively, geographic researchers are also unclear on what percentage of studies should be replicated. Like 'could be replicated', respondents on average say half of studies should be replicated (55.9\%, $sigma=27.7\%$), but with a large variance and fairly flat histogram that indicates overall disagreement on the value of replicating a lot of studies. 
\end{itemize}

Q8-11 Factors that affect the chances of replicating a claim.
Researchers collectively indicated that only a few study characteristics of phenomenon characteristics would alter an independent researcher's chances of replicating a prior claim. 
Researcher identified more study characteristics than phenomena characterstics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena. 
A small but notable percentage of researchers indicated that they simply did not know whether a factor would affect chances of replication.

@@

@@

\newpage
\bibliography{references}

\newpage
\noindent PETER KEDRON is an Associate Professor in the School of Geographical Science and Urban Planning and core faculty member in the Spatial Analysis Research Center (SPARC) at Arizona State University, Tempe, AZ, 85283, US. Email: Peter.Kedron@asu.edu. His research interests include spatial analysis, geographic information science, economic geography, and the accumulation of knowledge about geographic phenomena. \\

>>>>

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

\usepackage{tabularx}
\usepackage{booktabs,caption}
\usepackage{threeparttable}

\usepackage{lscape}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they had been hypothesized from the start of the research \citep{fraser2018questionable}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 17.7 percent, the response rate was 11.3 percent, yielding a cooperation rate of 64.0 percent. 
The refusal rate was 6.4 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly balanced across disciplinary subfields, but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%). 
Different methodological approaches were well represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
\begin{itemize}
    \item Respondents report thinking about replicability (73.9\%) talking with colleagues about replicability (65.0\%) and considering replicability when undertaking peer-review (59.0\%). 
    \item Far fewer respondents report attempting replications (31.8\%). 
\end{itemize}

\begin{itemize}
    \item Coded analysis of Q6
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Replication - Chances and motivations}
Overall geographic researchers believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of literature could or should be replicated (Figure \ref{fig:Q12-HCS}). 
On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
However, this average likely overstates the percentage of studies researchers believe have been replicated because the response distribution is strongly right skewed.
Our median response to this question is 20 percent and a heavy tail of containing 46.9 percent of responses estimated that less than 10 percent of recent studies have been replicated.
On average, respondents estimated that approximately half of studies 'could be replicated' (55.0\%) or 'should be replicated' (55.9\%). 
However, these averages are the product of the relatively flat distributions of estimates across the range of possible values. 
The response to both questions was also highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}) indicating no common knowledge or belief about the possibility or value of replicating recent work.

\begin{center}
\textbf{Insert Figure \ref{fig:Q12-HCS} About Here}
\end{center}

Q8-11 Factors that affect the chances of replicating a claim.
Researchers collectively indicated that only a few study characteristics of phenomenon characteristics would alter an independent researcher's chances of replicating a prior claim. 
Researcher identified more study characteristics than phenomena characteristics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena. 
A small but notable percentage of researchers indicated that they simply did not know whether a factor would affect chances of replication.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors that Affect the Decision to Attempt Replications}
Introductory para summarizing section and introducing Figure 2

\begin{center}
\textbf{Insert Figure \ref{fig:Q15-DecisionFactors} About Here}
\end{center}

Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt or not attempt a replication study. 
A majority of respondents identified the pressure to publish original research (77\%) and the lack of funding for replication studies (73\%) as frequently or always impacting the replication decision.
Respondents also believed that the perception of replications as low value work (64\%) that was often difficult to publish (63\%) impacted researcher decision making.  
Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
However, this finding should be interpreted with caution as a third of our respondents indicated that they did not know whether potential fabrication influenced researcher decision making.

Artifact Availability
\begin{itemize}
    \item See comment hanging off RE. That is the mains story on this one. 
\end{itemize}

Studt Characteristics
\begin{itemize}
    \item The characteristics of a study being replicated or the researcher attempting the replication were seen as less important by our respondents. 
    \item Respondents did not see ethical concerns as a inhibitor or replication studies.
\end{itemize}

\begin{center}
    \textbf{Insert Here Table \ref{tab:motivations}} 
\end{center}

Q16 - Include a presentation of the factors researchers identified that we did not include in the list of barriers.
\begin{itemize}
    \item Clerical issues related to field site access, costs, institutional approvals, 
    \item Lack of conceptual or methodological frameworks (how to measure similarity) to place RPLs in
    \item RPL is unnecessary in geog - (i) unique lens on world from each study is their main value, (ii) not valued across respondents from several disciplines and approaches.
    \item Instability of the system being studied across space and time - Replication is not possible in geography because of spatial heterogeneity or the study of one-off events, temporal variation.   
\end{itemize}

Q15 - A greater number of HG and QL responded that they did not know across all questions. Majority of QN researchers identified 'diff recreating proc' as impacting replication decision, minority for other groups. MM say 'low val of replication' as less impact on decision. HM and NS linked decision more to data access and recreation, while methods additionally linked to accessibility of methods info.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Replication Attempts}
\begin{itemize}
    \item sub-set demographics
    \item Q18 - same location response to characterize the attempts
    \item Q19 - Motivations
    \item Q20-21 - Replication outcome to component accessibility comparison. Perhaps also a comparison of success across locations by field of study (depending on the numbers).
    \item From Q21f percent that published their findings. The into Q22 why didn't respondents pursue publication.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliography{references}

\newpage
\begin{landscape}
\begin{table}[h]
    \centering
    \begin{threeparttable}
    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies }
    \begin{tabular}{l c c c c c c c c c c c c}
         \hline
                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & & & \\
         Barrier    & PH & MT & NS & HU            & & QN & MX & QL              & & Overall & N & Missing\\
         \hline
         \textit{Research Environment}      & & & & & & & & & & \\
         Pressure to original publish       & 72.6\% & 71.4\% & 64.3\% & 53.9\% & & 76.2\% & 63.7\% & 43.5\% & & 66.4\% & 245 & 38 \\
         Lack of funding for replication    & 64.6\% & 57.1\% & 69.0\% & 47.4\% & & 64.9\% & 59.8\% & 43.5\% & & 59.4\% & 231 & 51 \\
         Low perceived value                & 61.9\% & 59.5\% & 55.1\% & 42.1\% & & 64.9\% & 50.9\% & 36.9\% & & 55.2\% & 242 & 41 \\
         Difficulty publishing              & 50.5\% & 48.9\% & 57.1\% & 50.0\% & & 58.2\% & 47.1\% & 41.3\% & & 51.2\% & 231 & 51 \\
         Fraud                              & 17.6\% & 18.4\% & 23.8\% & 18.4\% & & 20.9\% & 21.6\% & 6.5\%  & & 18.7\% & 189 & 94 \\
                                            & & & & & & & & & & & & \\
         \textit{Artifact Availability}     & & & & & & & & & & & & \\
         Data inaccessibility               & 47.8\% & 57.1\% & 61.9\% & 43.9\% & & 56.7\% & 54.9\% & 41.3\% & & 53.7\% & 250 & 33 \\
         Lack of methods information        & 40.7\% & 59.2\% & 50.0\% & 40.8\% & & 50.0\% & 46.1\% & 30.4\% & & 44.6\% & 250 & 33 \\
         Inability to recreate procedure    & 38.1\% & 46.9\% & 40.4\% & 39.4\% & & 47.8\% & 36.3\% & 38.3\% & & 40.6\% & 246 & 37 \\
                                            & & & & & & & & & & & & \\
         \textit{Study/Researcher Characteristics}     & & & & & & & & & & & & \\
         Geographic variation               & 35.3\% & 32.7\% & 33.3\% & 27.7\% & & 31.4\% & 35.3\% & 36.4\% & & 32.5\% & 214 & 69 \\
         Inexperience with replication      & 27.4\% & 49.0\% & 50.0\% & 32.8\% & & 38.1\% & 37.3\% & 28.2\% & & 36.4\% & 229 & 54 \\
         Low probability of success         & 29.2\% & 31.6\% & 31.0\% & 29.0\% & & 30.6\% & 31.4\% & 28.3\% & & 30.4\% & 236 & 47 \\
         Ethical concerns                   & 10.5\% & 12.3\% & 21.4\% & 14.4\% & & 11.2\% & 18.6\% & 10.9\% & & 14.0\% & 218 & 68 \\
                                            & & & & & & & & & & & & \\
        \hline
    \end{tabular}
    \begin{tablenotes}
        \footnotesize
        \item Cells report the percentage of respondents reporting that a factor frequently, or always affect researchers' decision to attempt a replication of geographic research. Acronyms indicate: \textit{PH} Physical Geography, \textit{MT} GIScience and Methods, \textit{NS} Nature and Society, \textit{HU} Human Geography; \textit{QN} Quantitative, \textit{MX} Mixed Methods, \textit{QL} Qualitative. 
    \end{tablenotes}
    \label{tab:motivations}
    \end{threeparttable}
\end{table}
\end{landscape}

%%%%%%%%%%%%%%%%%%%%
\newpage

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.5]{results/figures/Fig-Q12-HCS.png}
    \caption{Estimates of the percentage of geographic studies that (a) have been replicated, (b) could be replicated, or (c) should be replicated}
    \label{fig:Q12-HCS}
\end{figure}

%%%%%%%%%%%%%%%%%%%%
\newpage

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}
    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies. Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC).}
    \label{fig:Q15-DecisionFactors}
\end{figure}

%%%%%%%%%%%%%%%%%%%%
\newpage
\noindent PETER KEDRON is an Associate Professor in the School of Geographical Science and Urban Planning and core faculty member in the Spatial Analysis Research Center (SPARC) at Arizona State University, Tempe, AZ, 85283, US. Email: Peter.Kedron@asu.edu. His research interests include spatial analysis, geographic information science, economic geography, and the accumulation of knowledge about geographic phenomena. \\
